Virtual Memory Assisted Transactional Memory for Dynamic Languages

### 2014-05-28 talk/dls2014/paper/paper.tex
add some no-jit performance graphs

\remi{For performance we first look at no-JIT behaviour of STM. Since
we cannot compete well even with CPython, we later show JIT benchmarks
where we see the unstable performance but also that we can still scale.
(with more work we can use our STM system to parallelise jitted code
too)}

more real benchmarks comparing multiple implementations:
\begin{itemize}[noitemsep]
\item pypy
\item pypy-jit
\item pypy-stm
\item pypy-stm-jit
\item cpython
\item jython
\end{itemize}

% TODO: Jython
\remi{Some benchmarks (figure \ref{fig:performance-jit} with enabled
JIT show that we can be competitive with the other solutions. It also
shows that more work is needed in that area to make performance more
stable.}

>>>>

\remi{For performance we first look at no-JIT behaviour of STM. Since
we cannot compete well even with CPython, we later show JIT benchmarks
where we see the unstable performance but also that we can still scale.
(with more work we can use our STM system to parallelise jitted code
too)} See figure \ref{fig:performance-nojit}

% TODO: pypy-nostm, Jython?
\begin{figure}[h]
  \centering
  \includegraphics[width=1\columnwidth]{plots/performance_nojit.pdf}
  \caption{Comparing runtime between interpreters without a JIT\label{fig:performance-nojit}}
\end{figure}

% TODO: Jython, compare to cpython? or just jython as common baseline with no-jit?
\remi{Some benchmarks (figure \ref{fig:performance-jit} with enabled
JIT show that we can be competitive with the other solutions. It also
shows that more work is needed in that area to make performance more
stable.}
